---
title: "Histone PTM profiling (ENCODE)"
author: "Florent Chuffart"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
---

```{r, echo=FALSE, eval=TRUE, label="loading libraries"}
knitr::opts_chunk$set(collapse=TRUE, comment = "#>", fig.width=9, fig.height=9, eval=TRUE, echo=FALSE, results="hide", dpi=150)
```

```{r, code = readLines("commons.R")}
```

# Features

```{r, code = readLines("loading_features.R")}
```

The purpose is to observe istone PTM profile of provided *features*

Provided *features* are: `r prefix`

# Heatmap of TSS PTM profiles of clusters

```{r echo=FALSE, results="verbatim"}
genes = readRDS("~/projects/genes/bed_grch38_epimeddb.rds")
features_ts = features[rownames(features) %in% rownames(genes)[genes$tss_cpg_status == "cpg_poor"],] 
dim(features)
set.seed(1)
rnd_features  = genes[sample(rownames(genes[genes$tss_cpg_status == "cpg_poor",]), 500),]
features_1 = features_ts [,1:6]  
features_2 = rnd_features [,1:6]   

cns = paste0("rndorts_", prefix)
features_1[[cns]] = "OLF"
features_2[[cns]] = "RND"
feat = rbind(features_1, features_2)
source(knitr::purl("00_deeptools_call.Rmd"))
```

deeptoolsr::dt_plot_heatmap("tmp/matrix_ewas_H3K27me3-human_rndorts_olfa.txt.gz", "tmp/hm_ewas_ewas_H3K27me3-human_rndorts_olfa_dsc.png", FORCE_EXEC=TRUE, sort_regions = "descend")
deeptoolsr::dt_plot_heatmap("tmp/matrix_ewas_H3K4me3-human_rndorts_olfa.txt.gz" , "tmp/hm_ewas_ewas_H3K4me3-human_rndorts_olfa_dsc.png" , FORCE_EXEC=TRUE, sort_regions = "descend")
deeptoolsr::dt_plot_heatmap("tmp/matrix_ewas_H3K27ac-human_rndorts_olfa.txt.gz" , "tmp/hm_ewas_ewas_H3K27ac-human_rndorts_olfa_dsc.png" , FORCE_EXEC=TRUE, sort_regions = "descend") 
deeptoolsr::dt_plot_heatmap("tmp/matrix_ewas_H3K4me1-human_rndorts_olfa.txt.gz" , "tmp/hm_ewas_ewas_H3K4me1-human_rndorts_olfa_dsc.png" , FORCE_EXEC=TRUE, sort_regions = "descend") 
deeptoolsr::dt_plot_heatmap("tmp/matrix_ewas_H3K9me3-human_rndorts_olfa.txt.gz" , "tmp/hm_ewas_ewas_H3K9me3-human_rndorts_olfa_dsc.png" , FORCE_EXEC=TRUE, sort_regions = "descend")




hm_filename = paste0(prefix, "_cpg_density_dsc.png")
deeptoolsr::dt_plot_heatmap(matrix_file, hm_filename, FORCE_EXEC=TRUE, sort_regions = "descend")








# Session Information

```{r, results="verbatim"}
sessionInfo()
```

